---
title: "COMPSCIX 415.2 Homework 3"
author: "Emerson Sosa"
date: "2/16/2019"
output: 
   html_document:
     theme: darkly
     highlight: espresso
     code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
```

## Libraries used:
```{r}
library(ggplot2)
library(nycflights13)
```




## Section 3.8.1 Exercises (all)
##

#### *1. What is the problem with this plot? How could you improve it?*

The problem with the first plot is that there are too many overlapping points on the graph. Using the <font color = "blue">`geom_jitter`</font> aesthetic allows for a more accurate illustration of the data.

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point() +
  ggtitle("Without jitter")
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter() +
  ggtitle("With jitter")
```



#### *2. What parameters to <font color = "blue">`geom_jitter()`</font> control the amount of jittering?*

Using <font color = "blue">`height`</font> and <font color = "blue">`width`</font> will adjust the spread parameters. If not used, jitter will be set to 40% of the resolution.

```{r}
?geom_jitter
```

#### *3. Compare and contrast <font color = "blue">`geom_jitter()`</font> with <font color = "blue">`geom_count`</font>.* 

The aesthetic <font color = "blue">`geom_jitter`</font> gives a spread around the same observation while <font color = "blue">`geom_count`</font> represents the overlapping values with area. A point that has at least 5 observations will have an area of 5 while a value that is observed at least 10 will have a corresponding area. 

```{r}
?geom_count
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter() +
  ggtitle("With jitter")
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
 geom_count() +
  ggtitle("With count")
```


#### *4. What's the default position for adjustment for <font color = "blue">`geom_boxplot()`</font>? Create a visualization of the `mpg` dataset that demonstrates it.*

By looking up the aesthetic via <font color = "blue">`?geom_boxplot`</font>, under the "Computed variables" section, it shows that the lower whisker is negative 1.5 X the interquartile range; the lower hinge is at the 25% quantile; middle is the median; upper hinge is the 75% quantile; ymax is positive 1.5 X the interquartile range.

The boxplot below shows the highway mpg for cars based on their wheel drive. The front wheel drive cars show the greatest mpg efficiency while 4 wheel drive and rear wheel drive are similar with rear wheel drive being more efficient and with less variability in obversations compared to 4 wheel drive. 

```{r}
?geom_boxplot
ggplot(mpg, aes(drv, hwy)) +
  geom_boxplot()
```


## Section 3.9.1 (2 and 4)

#### *2. What does <font color = "blue">`labs()`</font> do?*

<font color = "blue">`labs()`</font> gives the user the ability to add titles, subtitles, and captions to plots. 

```{r}
?labs
```

#### *4. What does the plot below tell you about the relationship between city and highway mpg? Why is <font color = "blue">`coord_fixed()`</font> important? What does <font color = "blue">`geom_abline()`</font> do?*

Using the <font color = "blue">`geom_abline`</font> as a reference where the slope is equal to 1, the plot shows that all cars have a higher mpg efficiency on the highway compared to the city (<font color = "blue">`geom_abline`</font> creates a slope of the graph and include an x intercept). As cars become more efficient overall, their efficiency is increased on the highway as well. In other words, cars that are efficient overall do even better on the highway. `coord_fixed() is important because it creates a one-to-one proportionality between the scale on the x and y axis. This is important in this graph because the unit of measure, miles, should be seen as equal on both scales. 

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() + 
  coord_fixed(ratio = 1) +
  ggtitle("With coord_fixed")

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() + 
  ggtitle("Without coord_fixed")
  
?coord_fixed
?geom_abline
```


## Section 4.4 (1 and 2)

#### *1. Why does this code not work?*

<font color = "blue">`
my_variable <- 10  
(my_varıable)  
`</font>

The code above does not work because we are calling a non-existent value because <font color = "blue">`my_varlable`</font> with an l has not been defined. Only `my_variable` with an i has. 

#### *2. Tweak each of the following R commands so that they run correctly:*

To run the code correctly, I had to correct `fliter` to `filter`, set a `==` to 8 as a singular `=` isn't recognized by R. The diamond data was also removed as we were using the mpg data set and not the diamond data set. 

```{r results='hide', message=FALSE, warning=FALSE}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
```


## Section 5.2.4 (1,3,4)

#### *1.1 Find all flights that had an arrival delay of two or more hours*

There were 10,190 flights that were delayed at by at least two hours.

```{r}
filter(flights, arr_delay >= 120 )
```

#### *1.2 Flew to Houston*

9,313 flights flew to Houston.

```{r}
filter(flights, dest == "IAH" | dest == "HOU")
```

#### *1.3 Were operated by United, American or Delta*

139,504 flights were run by either United, American, or Delta.

```{r}
distinct(flights, carrier)
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
```

#### *1.4 Departed in the summer*

86,326 flights departed in the summer.

```{r}
?flights
distinct(flights, month)
filter(flights, month == 7 | month == 8 | month == 9)
```


#### *1.5 Arrive more than two hours late, but didn't leave late*

Three flights fit the above criteria
```{r}
filter(flights, arr_delay >= 120 & dep_delay == 0)
```

#### *1.6 Were delayed by at least an hour but made up over 30 mintues in flight*

There were no flights that fit the above criteria but flight 51 was very close to achieving that. 

```{r}
select(filter(flights, dep_delay >= 60 & arr_delay < 0), flight, arr_delay)
```

#### *1.7 Departed between midnight and 6am*

9,344 flights departed between midnight and 6am.

```{r}
select(filter(flights, dep_time >= 0000 & dep_time <= 600), flight, dep_time)
```


#### * 3. How many flights have a missing `dep_time`? What other variables are missing? What might these rows represent?*

8,255 flights have a missing `dep_time` among other values. This is most likely canceled flights. 

```{r}
filter(flights, is.na(dep_time))
```


#### *4. Why is `NA ^ 0` not missing? Why is `NA | TRUE` not missing? Why is `FALSE & NA` not missing? Can you figure out the general rule? (`NA x 0` is a tricky counterexample!)*

`NA ^ 0` is not missing because any number to the zeroeth power is 1. `NA | TRUE` is not missing because we are assuming `NA` exists. The same is implied in `FALSE & NA`. Using `NA` assumes that a number does exist.

## Section 5.4.1 (1 and 3)

#### *1. Brainstorm as many ways as possible to select <font color = "blue">`dep_time`, `dep_delay`, `arr_time`</font>, and <font color = "blue">`arr_delay`</font> from flights.*

I don't really understand what the question is asking but I am assuming that it is asking the combinations in which the above variables can be called upon. You would just multiply the variables with each other to find the amount of variation, similar to a factorial. 

#### *3. What does the <font color = "blue">one_of()</font> function do? Why might it be helpful in conjunction with this vector?*

<font color = "blue">`vars <- c("year", "month", "day", "dep_delay", "arr_delay")`</font>

The <font color = "blue">`one_of`</font> function matches variable names in a character vector. This might be helpful when trying to match class types. 

```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, year, month, day, dep_delay, one_of(vars))
```


