---
title: "COMPSCIX 415.2 Homework 7"
author: "Emerson Sosa"
date: "3/12/2019"
output: 
   html_document:
     theme: darkly
     highlight: espresso
     code_folding: hide
     toc: true
     collapsed: true
     number_sections: false
     toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
```

<font color=#86efd3> </font>
<font color=#F38812 size=4> </font>

#<font color=#86efd3>Exercise 1</font> 

<font color=#F38812 size=4>*Load the train.csv dataset into R. How many observations and columns are there?*</font>

There are 1460 observations and 81 variables/columns.

```{r warning=FALSE, message=FALSE}
train.data <- 
  read_csv('train.csv')
glimpse(train.data)

```

#<font color=#86efd3>Exercise 2</font>

<font color=#F38812 size=4>*1. Visualize the distribution of SalePrice*</font>

```{r message=FALSE}
train.data %>% 
  ggplot() +
  geom_histogram(aes(SalePrice)) 
```


<font color=#F38812 size=4>*2. Visualize the covariation between SalePrice and Neighborhood.*</font>

```{r}
hood.and.price <- train.data %>% 
  group_by(Neighborhood) %>%
  summarise(SalePriceBar = median(SalePrice, na.rm = TRUE)) %>% 
  arrange(desc(SalePriceBar))

ggplot(hood.and.price) +
  geom_col(aes(Neighborhood, SalePriceBar)) +
  coord_flip()
```


<font color=#F38812 size=4>*3. Visualize the covariation between SalePrice and OverallQual.*</font>

```{r}
qual.and.price <- train.data %>% 
  group_by(OverallQual) %>%
  summarise(SalePriceBar = median(SalePrice, na.rm = TRUE))

ggplot(qual.and.price) +
  geom_col(aes(OverallQual, SalePriceBar)) +
  coord_flip()
```

#<font color=#86efd3>Exercise 3</font>

<font color=#F38812 size=4>*1. Take a look at the coefficient*</font>

The coefficient is 45436 when using Overall Quality as `x`.

```{r}
(train.lm <- lm(formula = SalePrice ~ OverallQual, data = train.data))
tidy(train.lm)
```


<font color=#F38812 size=4>*2. Compare the coefficient to the average value of SalePrice*</font>

The coefficient is much smaller than the coefficient.

```{r}
mean(train.data$SalePrice) 
train.lm
```


<font color=#F38812 size=4>*3. Take a look at the R-squared*</font>

The R squared is 0.63

```{r}
glance(train.lm)
```

#<font color=#86efd3>Exercise 4</font>

<font color=#F38812 size=4>*1. What kind of relationship will these features have with our target?*</font>

```{r}
diam_lm <- lm(formula = price ~ carat, data = diamonds)

diam_lm

```


<font color=#F38812 size=4>*2. Can the relationship be estimated linearly?*</font>

<font color=#F38812 size=4>*3. Are these good features, given the problem we are trying to solve?*</font>

<font color=#F38812 size=4>*4. How would you interpret the coefficients on GrLivArea and OverallQual?*</font>

<font color=#F38812 size=4>*5. How would you interpret the coefficient on NeighborhoodBrkSide?*</font>

<font color=#F38812 size=4>*6. Are the features significant?*</font>

<font color=#F38812 size=4>*7. Are the features practically significant?*</font>

<font color=#F38812 size=4>*8. Is the model a good fit?*</font>
