---
title: "COMPSCIX 415.2 Homework 4"
author: "Emerson Sosa"
date: "2/22/2019"
output: 
   html_document:
     theme: darkly
     highlight: espresso
     code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Libraries used:
```{r load_packages, warning=FALSE, message=FALSE}
library(ggplot2)
library(nycflights13)
library(tidyverse)
```

## Section 5.6.7

#### *2. Come up with another approach that will give you the same output as <font color = "blue">`not_cancelled %>% count(dest)`</font> and <font color = "blue">`not_cancelled %>% count(tailnum, wt = distance)`</font> (without using <font color = "blue">`count()`</font>.)*

```{r}
#defining not_cancelled
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

#using count()
not_cancelled %>% 
  count(dest)

#not using count()
not_cancelled %>%
  group_by(dest) %>%
  summarise(n = n())

#using count()
not_cancelled %>% 
  count(tailnum, wt = distance)

#not using count()
not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(n = sum(distance))
?flights
```

## *4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?*

The structure of this question made it very hard for me to understand what was being asked. Therefore, I drew up an analysis where I plotted all flights that were cancelled on an axis of months and days. I could not find any sort of pattern. I found this question to be extremely frustrating and I feel it is because I don't have a grasp on the code surrounding the summarise function.

```{r}

cancelled <- flights %>% 
  filter(is.na(dep_delay),
         is.na(arr_delay))
cancelled %>%
  count(month, day) %>% 
  ggplot(aes(month, day)) +
  geom_count() +
  geom_smooth(se = FALSE)
  
summarise(flights)
  
?summarise
```

#### *5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))*

#### *6. What does the sort argument to count() do. When might you use it?*

It would be useful when wanting to sort the count in order. 

```{r}
flights %>% 
  count(day)



flights %>%
  count(flight, sort = TRUE)

?sort()
```


## Section 10

#### *1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).*

A tibble would only display the first 10 rows and only the columns that fit on the screen. The first printed table does not truncate after 10 rows. 

```{r}
mtcars
as_tibble(mtcars)
```


#### *2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?*

Using a data.frame as compared to a tibble will potentially produce subsetting that is too general. When comparing the two below, the lax parsing behevior is evident in data.frame subsetting. 

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
df <- tibble(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

```


#### *3 If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?*

To extract a variable from a tibble, one must name the tibble, then call it using either the <font color = "blue">`$`</font> or <font color = "blue">`[[`</font> function. I attempted to use the <font color = "blue">`filter(var)`</font> function but it did not work and I am unsure why that is the case. 
```{r}
example <- tribble(
  ~var, ~ mpg, 
   1, 2, 1, 2
)  

example$var

```


#### *6. What option controls how many additional column names are printed at the footer of a tibble?*

Use <font color = "blue">`options(tibble.width = ())`</font> to denote how many columns or if you want to denote all columns regardless of screen size, inlcude <font color = "blue">`Inf`</font> in the denoter.

## Section 12.3.3

#### *2. Why does this code fail? <font color = "blue">`table4a %>% 
  gather(1999, 2000, key = "year", value = "cases")`</font>*
  
The code above did not work because it did not have the tick marks around the years. 

```{r}
(table4a <- tribble(
  ~country, ~`1999`, ~`2000`,
  #--|--|----
  "Afghanistan", 745, 2666,
  "Brazil", 37737, 80488,
  "China", 212258, 213766
))

table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases")
```


#### *3. Why does spreading this tibble fail? How could you add a new column to fix the problem?*

The spreading fails because Phillip Woods has two instances of age. I deleted the second instance of age for Phillip Woods to allow for proper spreading. It was not obvious why there were two instances of age

```{r}
library(tidyverse)
(people <- tribble(
  ~name, ~k, ~count, 
  #-----------------|--------|------
  "Phillip Woods", "age", 45, 
  "Phillip Woods", "height", 186, 
  
  "Jessica Cordero", "age", 37, 
  "Jessica Cordero", "height", 156
))

people %>% 
  spread(key = k, value = count)
```


#### *4. Tidy the simple tibble below. Do you need to spread or gather it? What are the variables?*

To tidy the data, it needs to be gathered. The variable are "pregnant", "sex", and "n".

```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)

preg %>% 
  gather(male, female, key ="sex", value = "n")
```


## Section 12.4.3

#### *1. What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets.*

They help fill in gaps and add values to a vector.

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop", fill = "right")

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop", fill = "right")


?separate
```


#### *2. Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?*

Per `?separate`, remove function removes the input column from the the output data frame. If you want to keep the input column, you would need to put false. 

```{r}
(tab4 <- table4a %>% 
  gather(`1999`, `2000`, key = "year", value = "cases"))

tab4 %>% 
  unite(whatev, year, cases, remove = TRUE)
```

## Uploading and exporting flat files:

```{r}
library(tidyverse)
file_path <- 'flights.csv'
csv_data <- read_csv(file = file_path)

glimpse(csv_data)

write_delim(csv_data, delim = '|', path = 'baby_names.csv')

baby_path <- 'baby_names.csv'
baby_data <- read_csv(file = baby_path)

glimpse(baby_data)

?write_csv
```

