---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Emerson Sosa"
date: "3/2/2019"
output: 
   html_document:
     theme: darkly
     highlight: espresso
     code_folding: hide
     toc: true
     collapsed: true
     number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<font color=blue> </font>
<font color=#873f05> </font>

# <font color=#873f05>The tidyverse packages</font>

#### *Can you name which package is associated with each task below?*


1. Plotting: For plotting, use the <font color=blue>`ggplot2`</font> package.
2. Data munging/wrangling: For data wrangling use the <font color=blue>`dplyr`</font> package.
3. Reshaping data: To reshape the data use the <font color=blue>`tidyr`</font> package.?
4. Importing/exporting data: For importing and exporting, use the <font color=blue>`readr`</font> package.

#### *Now can you name two functions that you've used from each package that you listed above for these tasks?*

1. Plotting: In conjunction with <font color=blue>`ggplot2`</font>, I have used the <font color=blue>`geom_point()`</font> and <font color=blue>`geom_count()`</font> for visualizing data. 
2. Data munging/wrangling: The <font color=blue>`filter()`</font> function has been very useful for me and I have admired the power of the <font color=blue>`summarise()`</font> when used with the <font color=blue>`group_by()`</font> function.
3. Reshaping data: Understanding the usage of <font color=blue>`gather()`</font> and <font color=blue>`spread()`</font> will be essential when colloborating with others as it cannot be assumed that they will be using tidy data. 
4. Importing/exporting data: To import data, use <font color=blue>`read_csv()`</font> to import and <font color=blue>`write_csv()`</font> to export as a csv. file. 

# <font color=#873f05>R Basics</font>

#### *1. Fix this code with the fewest number of changes possible so it works:*

I added quote marks around the tag to allow the exclamation point.

```{r}
('My_data.name___is.too00ooLong!' <- c( 1 , 2   , 3 ))
```


#### *2. Fix this code so it works:*

To fix, I changed the case of the concatenation function to lower case and added a quote end mark to <i>it</i>.

```{r}
(my_string <- c('has', 'an', 'error', 'in', 'it'))
```


#### *3. Look at the code below and comment on what happened to the values in the vector.*

R does not need quotes around numbers when making them a vector. When quotes are placed around them, R forces the exact input inside. For example, if a space is placed inside the quote marks, r will print that extra space as well. The same is not true when adding extra spaces to numbers without quotes around the number. 

```{r}
my_vector <- c(1,2, '3', '4', 5)
my_vector
```




