---
title: "HW 2"
author: "Emerson Sosa"
date: "2/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.2.4 Exercises

1. When running ggplot(data = mpg), only a blank graph is displayed. 
2. There are 234 rows and 11 columns in mpg.
3. Vairable drv describes what type of wheel drive the car has: e.g., front wheel drive (f), rear wheel drive (r), or four wheel drive (4wd).
4. see graph below
5. Plotting class and drv variables are not useful because they are both categorical and are not continous. 
```{r}
library(ggplot2)
ggplot(data = mpg) + ggtitle("Question #1")
mpg
?mpg
ggplot(data = mpg) + geom_point(mapping = aes(x =hwy, y = cyl)) + ggtitle("Question #4")
ggplot(data = mpg) + geom_point(mapping = aes(x =class, y = drv)) + ggtitle("Question #5")
```

## 3.3.1 Exercises

1. The points are not blue because ggplot is looking for data in the third position where color = "blue" is. If one would like the points to be blue, one would have to close the aes argument and + the color blue outside of it: e.g., geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
2. Manufacturer, model, cyl, trans, drv, fuel type, class are categorical. Displ, year, cty, hwy are continuous. One can gauge this when by seeing what are the headers for the columns and seeing whether the data in the rows are numbers or words. There are exceptions to this as a categories can be made up of discrete numbers. 
3. Shape cannot be mapped to a continous variable due to its nature of not being a continuous aesthetic. For continuous variables, it would be better to use aesthetics such as color and size but the same is not true for categorical variables, possibly. 
4. Mapping several aesthetics to a single continuous variable compounds their effects on each other. 
5. The stroke aesthetic modifies the width of the border. Stroke generally works with all shapes but for detailed shapes such as 8, 10, 12, 13, resolution is lost when increasing stroke. 
6. When using (in)equalities to map variables, it creates two classes based on whether the argument is fulfilled. In this case, cars with a displacement lower than 5 have been colored blue. 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cty)) + ggtitle("Question 3: Using color as a continuous variable")
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = cty)) + ggtitle("Question 3: Using size as a continuous variable")
ggplot(data = mpg) + ggtitle("Question 3: Using shape as a continuous variable \nBlank due to error when running")
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy, size = cty, color = cty, stroke = cty)) + ggtitle("Question 3: Using multiple aesthetics for a single variable")
?geom_point
ggplot(data = mpg) +
geom_point(mapping = aes(x = drv, y = class), shape = 1, stroke = 10) + ggtitle("Question 5: Using shapes and strokes")
ggplot(data = mpg) +
geom_point(mapping = aes(x = drv, y = class), shape = 3, stroke = 10) + ggtitle("Question 5: Using shapes and strokes")
ggplot(data = mpg) +
geom_point(mapping = aes(x = drv, y = class), shape = 13, stroke = 10) + ggtitle("Question 5: Using shapes and strokes")
ggplot(data = mpg) +
geom_point(mapping = aes(x = drv, y = class), shape = 21, stroke = 10) + ggtitle("Question 5: Using shapes and strokes")
ggplot(data = mpg) +
geom_point(mapping = aes(x = cty, y = displ)) + ggtitle("Question 6: Mapping to something else") +
aes(colour = displ < 5) + theme_void()
```

## 3.5.1 Exercises

4. The advantages to using the facet function compared to the color function is that it is easier to analyze each variable individually. When the color function is used for a data set that has a lot of categorical variables, it will be harder to distinguish between them. Even for continuous variables, there will come a point where using color will not be useful in distinguishing minute differences in the data. 
5. nrow is able to list how may rows of grpahs are displayed. ncol does the same for the columns. One is able to also shrink scales to fit data, rank tables, and switch labelling. facet_grid() does not have nrow or ncol because ggplot creates the columns and rows automatically to make efficient the use of columns and rows.  
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2, as.table = TRUE)
?facet_wrap
```

## 3.6.1 Exercises

1. For line charts, use geom_abline, geom_hline, or geom_vline. For a boxplot, use geom_boxplot. For histogram, use geom_histogram. For area chart, use geom_area. 
2. I predict that displacement, highway mpg, and wheel drive will be plotted in a point graph and on a regressional line.
3. show.legend = FALSE is supposed to suppress legend illustration although I could not get it to work. 
4. By running ?geom_smooth, I can see that se enables a confidence interval for the line. 
5. The graphs will look the same because they are both graphing the same data and variables. The first code is more efficient however because the data is mapped first, then the layers are added via open mapping underneath -> ()
6. (extra credit)

```{r}
?geom_smooth
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv, show.legend = FALSE)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + ggtitle("Question #2")
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth() + ggtitle("Question #5 comparison")

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy)) + ggtitle("Question #5 comparison")
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(stroke = 2) + 
  geom_smooth(se = FALSE) + ggtitle("Question #6.1")
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv), se = FALSE) +
  geom_point(mapping = aes(x = displ, y = hwy, stroke = 2)) +   ggtitle("Question #6.2")
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv, color = drv), se = FALSE) +
  geom_point(mapping = aes(x = displ, y = hwy, stroke = 2, color = drv)) +   ggtitle("Question #6.3")
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = drv, stroke = 2)) + 
  geom_smooth(se = FALSE)+ ggtitle("Question #6.4")
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = drv, stroke = 2)) + 
 geom_smooth(mapping = aes(linetype = drv), se = FALSE) + ggtitle("Question #6.5")
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = drv, stroke = 2, ))  +
  geom_point(shape = 1, size = 12,colour = "white", fill = "white") +
  ggtitle("Question #6.6")
```


## 3.7.1 Exercises

2.geom_bar() makes the height of the bar proportional to the number of cases in each group (or if the weight aesthetic is supplied, the sum of the weights). If you want the heights of the bars to represent values in the data, use geom_col() instead

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop..))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..prop..))
```

## Last question

In https://static.guim.co.uk/sys-images/Guardian/Pix/pictures/2012/3/2/1330695817953/EMC2-graphic-on-data-scie-008.jpg, the consistency of the color pallete is professional. The fact that the format is presented in a vertical jpeg is weird and tough to zoom into. The first graphic uses a pie chart which is not good for discerning differences between the categories. It seems as thought the data scientist wanted to present a wide variety of data graphs and in doing so, sacrificed a clear presentation for some. There was nice usage of the alpha presenter when showing the percent of what the biggest obstacle to data science adoptation. The last graphic is peculiar as well because a color pallete is used to discriminate the categories in an arbitrary fashion where a bar graph would be more effective since there seems to be a significant difference when looking at the graphic designer category. 